\chapter{Introduction}%
\label{ch:intro}%

\nv{%
In this section, I'll try to portray my ``elevator pitch''.

\textbf{Pitch:}
\begin{enumerate}
    \item \label{item:pitch1} What is the problem this thesis is trying to solve?
        \begin{itemize}
            \item a
        \end{itemize}
    \item Why is the problem an important one to analyse?
        \begin{itemize}
            \item a
        \end{itemize}
    \item Give a positive and bold statement of what this thesis is doing.
        \textbf{If nothing else is remembered from the thesis, this should be it.}
        \begin{itemize}
            \item a
        \end{itemize}
    \item The consequences of the thesis (preferrably ``solve'' the problem
        in~\ref{item:pitch1})
        \begin{itemize}
            \item a
        \end{itemize}
\end{enumerate}

\subsection*{Embedded Cyber-Physical Systems}%
%
Figure (somewhere) of a general embedded setup with a brief introduction to the different
parts of the figure (nothing technical).

\textbf{The What:}
\begin{itemize}
    \item Connectivity, Distributed systems, NCS, IoT, Wireless
    \item Communication hickups
    \item packet drops
    \item deadline misses
\end{itemize}

\textbf{The why:}
\begin{itemize}
    \item Huge costs, damages
    \item Safety
    \item Security
    \item Paper by~\cite{Akesson:2020}
\end{itemize}

\subsection*{Control Theoretical Benefits}%
%
Short introduction to what has historically been done to mitigate the problems

\textbf{The Statement:}
\begin{itemize}
    \item Theoretical and practical tools for analysing and synthesising
        fault-tolerant controllers, with significant performance gains.
    \item Lowering the entry-level knowledge for applying the tools to real
        processes.
\end{itemize}

\textbf{The Consequences:}
\begin{itemize}
    \item Decoupling and clarifying real-time and control theoretical models.
    \item Making them more accessible to a broader class of practictioners.
\end{itemize}

\subsection*{Outline}%
%
Thesis outline.
}%
