\chapter*{Acknowledgements}
I would like to begin by expressing my deepest gratitude to everyone who has contributed to my journey towards a PhD, both professionally and personally.
While it is impossible to mention everyone by name, I am immensely grateful to those who have brightened my days and helped me along the way.

Firstly, I owe a special thanks to the Department of Automatic Control and the many individuals who have made it such a welcoming and supportive workspace.
Were it not for the people there, I would never have pursued a PhD.
A special mention goes out to: Gautham, Mattias, Bagge, Martinka, Marcus TA, Marcus G, Pauline, Victor, Alex, Max NC, Johanna W, Frida N, Luka, and the Innebandy Crew.
%Finally, 
Another important reason why the department is such a pleasant workspace are the tireless efforts of Eva, Mika, Cecilia, Monika, Anders B, and Anders N.
Thank you for providing invaluable support to all the PhD students passing through the department, all while spreading joy.

A special thank you is extended to my supervisor and dear friend, Martina.
Your constant support, both professionally and personally, has been invaluable to me, and I would not be the person I am today without you.
Words cannot express my gratitude, but please know that I will be forever grateful for having shared this journey with you.
And to my co-supervisor and mentor, Anton, your encouragement during times of doubt has been instrumental in me reaching my goal.
Thank you for all the beers shared, and to many more.

I am fortunate to count many of my colleagues as close friends.
Claudio, thank you for sticking by me through thick and thin, and for all the unforgettable work discussions, life events, drinking nights, and travels.
Ylva, I am thankful for your encouragement, your friendship, and the many meaningful conversations we have had (and will have) over dinners and game nights.
Albin, Martin H, and Martin M, you have all been an inspiration (even in the face of adversity), and I am grateful for the laughter, dinners, pub nights, and game nights we have shared, and to the ones to come.
Paolo, your kindness and knowledge have helped guide me, and I am lucky to have had the pleasure of getting to know you.
Johan R, thank you for all the pub nights and trips we have enjoyed together.
And finally, to Richard, thank you for for always having my back and for the joy you bring.

Last but not least, I am forever grateful for the love and support of my friends and family outside of work who have encouraged me throughout my journey towards a PhD.
Calle, you have always been there for me, whether we were living together or not, and I appreciate all the new and cool things you have taught me, and the good times we have shared.
To Olof and Erik B, despite us seeing each other far too rarely, I cannot thank you enough for your friendship.
And to my parents, who may not always have understood the details of my work, but have always stood by me with unwavering support and love; thank you!
To my brother Kalle, you have been a constant inspiration to me, and I am so lucky to have you in my life.
And finally, to Elin, there are no words to thank you enough, and to {\AA}se and Micke, your support means the world to me.

\subsubsection*{Financial Support}
The author is a member of the ELLIIT Strategic Research Area at Lund University.
This project has received funding from the European Union's Horizon 2020 research and innovation programme under grant agreement Number 871259 (ADMORPH project).
This publication reflects only the author's view and the European Commission is not responsible for any use that may be made of the information it contains.
